The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Small changes to paper

This implies that when searching for the maximal exponent defining {\tt nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of {\tt nu(e-1,I,J)}, and one needn't search too far past this number.  This also suggests that the most efficient way to compute {\tt nu(e,I,J)} is to compute, successively, {\tt nu(s,I,J)}, for each integer $s = 0,\ldots,e$.  This is indeed how the computation is done in most cases.

@@

If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the four forementioned cases, then the function {\tt fpt} next calls {\tt isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing.  If this command returns {\tt true}, the $F$-pure threshold can easily be computed, and {\tt fpt} returns this value.  For more detail on the function {\tt isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see Section \ref{subsec.SNC}.

\subsection{How {\tt fpt} proceeds when no special algorithm applies}

@@

If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval.
First, a number in the interval is selected, according to criteria specified by the value of the option {\tt GuessStrategy}; we refer the reader for the documentation of this option for more details.
Then the function {\tt compareFPT} is used to test that number. If that "guess" is correct, its value is returned; otherwise, the data returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.

@@

\subsection{The function {\tt isSimpleNormalCrossings}} \label{subsec.SNC}
As mentioned earlier,
when the option {\tt useSpecialFunctions} for the function {\tt fpt} is set to {\tt true}, if the polynomial $f$ is neither a diagonal polynomial, a binomial, or a form in two variables, there is a final check to verify whether $f$ is a product of factors in simple normal crossing.

Suppose that $f$ has factorization $f_1^{a_i} f_2^{a_2} \cdots f_n^{a_n}$.  Recall that its factors $f_i$ are said to be in
\emph{simple normal crossing} at a point if, locally, they form part of a regular system of parameters.  The function {\tt isSimpleNormalCrossings} determines whether $f$ has simple normal crossings by computing the Jacobian matrix of each subset of $\{ f_i \}_{i=1}^n$ (evaluated at the origin), and checking that these matrices have the expected rank, and that these subsets generate ideals of the appropriate height.

@@

\begin{enumerate}
\item Add more cases to {\tt UseSpecialAlgorithms}.
%\item Add the capability to compute non-local {\tt fpt} and non-local {\tt nu} via an option.
\item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.

@@

\newpage
\bibliographystyle{skalpha}
\bibliography{MainBib}

>>>>

This implies that when searching for the maximal exponent defining {\tt nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of {\tt nu(e-1,I,J)}, and one needn't search too far past this number.  This also suggests that the most efficient way to compute {\tt nu(e,I,J)} is to compute, successively, {\tt nu(s,I,J)}, for each $s = 0,\ldots,e$.  This is indeed how the computation is done in most cases.

@@

If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the aforementioned cases, then the function {\tt fpt} next calls {\tt isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing, in which case the $F$-pure threshold can easily be computed.
For more detail on the function {\tt isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see Section \ref{subsec.SNC}.

\subsection{When no special algorithm applies}

@@

If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval.
First, a number in the interval is selected, according to criteria specified by the value of the option {\tt GuessStrategy}; we refer the reader for the documentation of this option for more details.
Then the function {\tt compareFPT} is used to test that number. If that ``guess'' is correct, its value is returned; otherwise, the data returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.

@@

\subsection{The function {\tt isSimpleNormalCrossings}} \label{subsec.SNC}
As mentioned earlier, the function {\tt isSimpleNormalCrossings} verifies whether $f$ is a product of factors in simple normal crossing.
Suppose that $f$ has factorization $f_1^{a_i} f_2^{a_2} \cdots f_n^{a_n}$.  Recall that its factors $f_i$ are said to be in
\emph{simple normal crossing} at a point if, locally, they form part of a regular system of parameters.  The function {\tt isSimpleNormalCrossings} determines whether $f$ has simple normal crossings by computing the Jacobian matrix of each subset of $\{ f_i \}_{i=1}^n$ (evaluated at the origin), and checking that these matrices have the expected rank, and that these subsets generate ideals of the appropriate height.

@@

\begin{enumerate}
\item Add more cases to {\tt UseSpecialAlgorithms}.
\item Add the capability to compute non-local {\tt fpt} and non-local {\tt nu} via an option.
\item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.

@@

\bibliographystyle{skalpha}
\bibliography{MainBib}
